SST_patterns

### 2019-11-05 SST_patterns.Rmd
update

Loading the data
```{r}
load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
```

@@

# ANOVA
- Relationship between duration, year and site as a function of the distance

@@

load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")

@@

@@

CMC_filtered <- year_func(df = CMC_upwell_base)
OISST_filtered <- year_func(df = OISST_upwell_base)
SACTN_filtered <- year_func(df = SACTN_upwell_base)

@@

MUR_filtered <- year_func(df = MUR_upwell_base)

MUR_SEAPOINT <- MUR_filtered %>% 
  filter(site == "Sea Point")
MUR_SB <- MUR_filtered %>% 
  filter(site == "Saldanha Bay")
MUR_PN <- MUR_filtered %>% 
  filter(site == "Port Nolloth")
MUR_LB <- MUR_filtered %>% 
  filter(site == "Lamberts Bay")
```

@@

combined_MUR_pl_1 <- ggarrange(MUR_LB_pl, MUR_PN_pl)

>>>>

Loading the data
```{r}
load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
load("Data/G1SST_upwell_base.RData")
```

@@

# ANOVA
- Relationship between duration, year and site as a function of the distance 
The number of events per distance and then compare this at each distance

@@

load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
load("Data/G1SST_upwell_base.RData")

@@

G1SST_upwell_base <- km_func(df = G1SST_upwell_base)
G1SST_upwell_base$distance_km <- as.numeric(G1SST_upwell_base$distance_km)

@@

CMC_filtered <- year_func(df = CMC_upwell_base)
OISST_filtered <- year_func(df = OISST_upwell_base)
SACTN_filtered <- year_func(df = SACTN_upwell_base)
MUR_filtered <- year_func(df = MUR_upwell_base)
G1SST_filtered <- year_func(df = G1SST_upwell_base)

@@

MUR_SEAPOINT <- MUR_filtered %>% 
  filter(site == "Sea Point")
MUR_SB <- MUR_filtered %>% 
  filter(site == "Saldanha Bay")
MUR_PN <- MUR_filtered %>% 
  filter(site == "Port Nolloth")
MUR_LB <- MUR_filtered %>% 
  filter(site == "Lamberts Bay")
###########
####G1SST

G1SST_SEAPOINT <- G1SST_filtered %>% 
  filter(site == "Sea Point")
G1SST_SB <- G1SST_filtered %>% 
  filter(site == "Saldanha Bay")
G1SST_PN <- G1SST_filtered %>% 
  filter(site == "Port Nolloth")
G1SST_LB <- G1SST_filtered %>% 
  filter(site == "Lamberts Bay")

@@

combined_MUR_pl_1 <- ggarrange(MUR_LB_pl, MUR_PN_pl)
#######
#G1SST
